\chapter{Introduction}
\label{chap:intro}

Notification Systems are tools specifically designed to provide the users with informative content instantaneously sent from secondary applications. Due to the tremendous amount of applications now in the market and the randomness of the notifications that are being sent. Users are getting more likely affected negatively in their primary tasks in a lot of manners like negative effects on their task completion time, error rate, annoyance and anxiety.

As notifications have different cost of interruption. We need to quantify this cost as well as show awareness messages to the user in suitable manner. Taking the challenge of integrating the massive bio-sensors field in the identification of the cost of notifications interruption.

\begin{itemize}
  \item Recording Eye Gaze movement while working on a specific task
  \item Thus propose different solutions and information whether visually of using alarming systems to let the users understand their state and how it's changed with the interruptions along the time. Users will then have a better understanding of their performance curves and how it is negatively being affected by these interruptions and distractions.
  \item To understand if the process has a positive effect on the users or not. We will test on two different types of users with the same workload, One of them is working using our interruption awareness system and the other is not using it.
\end{itemize}

If enhancements of time management and productivity appears on our first group, this will prove that our approach is correct and that notification management is a challenge for productivity and time management.